Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization

### 2021-12-13 Final Draft/Final Draft.Rmd
dataverse and table row names

---
title: "Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization"
short: "Brother, Can You Spare a Manufacturing Job? "
month: "`r format(Sys.Date(), '%m')`"
year: "`r format(Sys.Date(), '%Y')`"
author:
  - name: Catherine Darin
    firstname: Catherine
    surname: Darin
    email: cdarin@hks.harvard.edu
    affiliation: Harvard University
  - name: Zagreb Mukerjee
    firstname: Zagreb
    surname: Mukerjee
    email: zagrebmukerjee@fas.harvard.edu
    affiliation: Harvard University
acknowledgements: | 
  Code available at https://github.com/zagrebmukerjee/ReplicationPaper
abstract: |
    What led to Donald Trump's surprising 2016 election victory? This paper examines the potential contribution of deindustrialization. We exploit county-level differences in manufacturing density as a source of exogenous variation, using both instrumental-variable regression and covariate balancing methods. Counter-intuitively, we find that counties that gained manufacturing jobs from 2012-2015 are more likely to have swung towards Trump. We believe this is due to an omitted variable - the job loss experienced from 2004 to 2012. Counties that experienced prior deindustrialization were more likely to exhibit increased support for Trump, as well as a slight manufacturing rebound in 2012-2015. Dis-aggregating this result by race shows that the Democratic vote share fell where job losses affected white populations, and rose where job losses affected nonwhites. This suggests a racial component to how voters process economic hardship.
output: rticles::aea_article
header-includes: 
 - \usepackage{graphicx}
 - \usepackage{amsmath}
 - \usepackage{amssymb}
 - \usepackage{placeins}
---

>>>>

---
title: "Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization"
short: "Brother, Can You Spare a Manufacturing Job? "
month: "`r format(Sys.Date(), '%m')`"
year: "`r format(Sys.Date(), '%Y')`"
author:
  - name: Catherine Darin
    firstname: Catherine
    surname: Darin
    email: cdarin@hks.harvard.edu
    affiliation: Harvard University
  - name: Zagreb Mukerjee
    firstname: Zagreb
    surname: Mukerjee
    email: zagrebmukerjee@fas.harvard.edu
    affiliation: Harvard University
acknowledgements: | 
  Code available at https://github.com/zagrebmukerjee/ReplicationPaper; https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/7U2UIQ
abstract: |
    What led to Donald Trump's surprising 2016 election victory? This paper examines the potential contribution of deindustrialization. We exploit county-level differences in manufacturing density as a source of exogenous variation, using both instrumental-variable regression and covariate balancing methods. Counter-intuitively, we find that counties that gained manufacturing jobs from 2012-2015 are more likely to have swung towards Trump. We believe this is due to an omitted variable - the job loss experienced from 2004 to 2012. Counties that experienced prior deindustrialization were more likely to exhibit increased support for Trump, as well as a slight manufacturing rebound in 2012-2015. Dis-aggregating this result by race shows that the Democratic vote share fell where job losses affected white populations, and rose where job losses affected nonwhites. This suggests a racial component to how voters process economic hardship.
output: rticles::aea_article
header-includes: 
 - \usepackage{graphicx}
 - \usepackage{amsmath}
 - \usepackage{amssymb}
 - \usepackage{placeins}
---
